An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Fleshed out invariance in ones direction

\begin{assumption} \label{assume:cal}
  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
  The embedding points are $\{u_r : r \in \R\}$.
\end{assumption}

Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
For each $U \in \U$, let $R_U = \{r: r_u \in U\}$.

@@

  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
  This implies that $u_r$, the embedding point, is optimal for $p$, so $u_r \in U$.
  This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
\end{proof}

@@

@@

Let $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$.
We next see that $\U$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
\end{lemma}
\begin{proof}
  First, observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.

@@

  Substituting these values into the expected loss, we now observe a linear objective over the hypercube, which is known to be optimal on some corner of the hypercube, so the rest of $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
  Therefore, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
  Moreover, for this optimal $u$, observe $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$.
\end{proof}

>>>>

\begin{assumption} \label{assume:cal}
  $\ell: \R \times \Y \to \reals^{\Y}_+$ is a loss on a finite report set $\R$, eliciting the property $\gamma: \simplex \toto \R$.
  It is embedded by $L: \reals^d \times \Y \to \reals^{\Y}_+$, which elicits the property $\Gamma: \simplex \toto \reals^d$.
  The embedding points are $\{\varphi(r) : r \in \R\}$.
\end{assumption}

Given Assumption \ref{assume:cal}, let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.
Let $\U \subseteq 2^{\reals^d}$ be defined as $\U = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
For each $U \in \U$, let $R_U = \{r: \varphi(r) \in U\}$.

@@

  For each $U \in \U'$, for any $p$ such that $U = \Gamma(p)$, we have in particular that $u$ is optimal for $p$, so $p \in \Gamma_u$, so $p \in \gamma_r$, so $r$ is optimal for $p$.
  This implies that $\phi(r)$, the embedding point, is optimal for $p$, so $\phi(r) \in U$.
  This holds for all $U \in \U'$, so $r \in \cap_{U\in\U'} R_U$, so it is nonempty.
\end{proof}

@@

In the rest of the section, for shorthand, we write $L(u;p) := \langle p, L(u) \rangle$ and similarly $\ell(r;p)$.

@@

Let $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$.
We next see that $\U$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
\end{lemma}
\begin{proof}
  First, observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
  To see this,
  \begin{align*}
  L'(u + \alpha \ones)_y &=\left(\frac{1}{k} \sum_{i=1}^k ((u+\alpha \ones) + \ones - e_y)_{[i]} - (u_y + \alpha) \right)_+\\
  &= \left(\frac{1}{k} \left[k\alpha + \sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
  &= \left(\alpha + \frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
  &= \left(\frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - u_y \right)_+\\
  &= L(u)_y
  \end{align*}

@@

  Substituting these values into the expected loss, we now observe a linear objective over the hypercube, which is known to be optimal on some corner of the hypercube, so the rest of $u_{[1]}, u_{[2]}, \ldots, u_{[k]} \in \{0,1\}$.
  Therefore, for all $p \in \simplex$, there is a report $u \in \{0,1\}^n$ optimizing $L'$.
  Moreover, for this optimal $u$, observe $\|u\|_{1} \leq k$ since we have $u_{[k+1]} = u_{[k+2]} = \ldots = u_{[n]} = 0$, so we observe that $u \in \U$ as well.
\end{proof}
